Does personal relevance attenuate citizens' persuasion by government branding? Evidence from a survey experiment on air-pollution policy

### 2019-07-25 paper3_revision_text.Rmd
Add files via upload

Viewed against the above theoretical framework, symbolic elements in government communications can be regarded as peripheral cues, which can affect citizens' attitudes though a peripheral route process of evaluative conditioning.[^footnote_symbols_arguments] Hence, based on ELM, citizens judgements about public organizations are less likely to be affected by symbols (and more likely to be shaped by substantive arguments) the more motivated they are to critically think about the message. Their level of motivation is likely to be determined, to a great extent, by their perceived personal relevnace of the particular policy issue.

@@

*H<sub>1</sub> - Symbolic elements in communications are likely to have a greater positive effect on citizens' attitudes about government organizations and policies, the less citizens perceive the policy issue in the communication as having personal relevance for themselves.*

*H<sub>2</sub> - The argument quality of the information in communications is likely to have a lesser effect on citizens' attitudes about government organizations and policies, the less citizens perceive the policy issue in the communication as having personal relevance for themselves.*

@@

While comparing those residing in the Haifa Bay to others enables me to examine the moderating effect of perceived personal relevance, it still has an important limitation - it represents an observational comparison. The differences in personal relevance can be theoretically confounded by unobserved covariates, that cannot be effectively controlled in the analyses. I address this limitation in the research design in three main ways. *First*, in the selection of the research population, I sought to reduce differences in socioeconomic and demographic variables between residents of Haifa Bay, and their comparison group. Accordingly, I selected the major cities in the Haifa Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*,[^footnote_qiryat-Hayiim] *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*). The socioeconomic characteristics of these selected cities are summarized in the supplementary appendix (section ##). To ensure that the two groups would differ in relation to the their perceptions about the relevance air-pollution policies, I searched relevant EPM documents and news websites and confirmed that there no particular reporting about high air-pollution levels in the three center cities.

*Second*, in addition to the policy regarding the air-pollution in Haifa Bay, I also included in the experiment a second policy plan that is expected to be perceived by the two groups as equally relevant. For this purpose, I selected a policy plan of EPM that regards *reducing domestic waste and increasing recycling*. The comparison between the two EPM policies is intended to confirm that respondents’ divergent responses to symbolic elements in the communication of the first policy, if found, are attributed to differences in perceived personal relevance, and not to other covariates. I henceforth refer to these two policy plans as "air-pollution" and "recycling". *Third*, in addition to the observational comparison between the two areas, I also included an experimental manipulation aimed at enhancing the perceived personal relevance of the air-pollution policy among the Haifa Bay residents.

@@

[^footnote_relevance_manipulation]: The first three treatment questions were also initially designed to prime subjects, more generally, to think about the impact of environmental issues to their own lives. In this paper, I focus on the the moderating effect of the relevance manipulation on Haifa Bay citizens' responses to the air-pollution policy.

Participants were then presented with the air-pollution and recycling policy plans (displayed in a random order). They were informed that these plans were obtained from EPM's annual work plan. The participants were randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols manipulation): treatment ("real symbols"), control-"no symbols" and control-"fake symbols". In the real symbols condition, the two policies are displayed with three symbolic brand elements, which have been used in EPM's public communications, and became widely recognized by the public. The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment. The second element is the green color, which is strongly associated with taking care of the environment. The third element is an image of a celebrity comedian from an advertising campaign of the EPM. The air-pollution policy (in the real symbols condition) was presented with an image from EPM campaign from 2010 under the slogan "starting to think green", starring the Israeli celebrity comedian Tal Friedman. The recycling policy (in the real symbols condition) was presented with an image from a campaign from 2017 for reducing the use of disposable bags ("taking every bag seriously"), starring the comedian Ido Rosenblum. In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities’ images. Finally, in the control fake-symbols condition, the EPM logo is replaced by a fake logo, the green color is replaced with blue, and the images of celebrities from the campaigns are replaced with edited images of unfamiliar people. The purpose of the fake-logo condition was to distinguish the effect of the symbolic meaning of the EPM's graphic brand elements (i.e. the symbolic effect) from a possible effect of their aesthetic design. Accordingly, I specifically designed the "fake" symbols so that they would resemble the real symbols and have equivalent aesthetic qualities, without activating particular emotions and associations related to EPM, or environmental policy. The symbols conditions are displayed in **Appendix B**. Further details about the real and fake symbols are found in section ## of the supplementary appendix.

In addition, I also included a manipulation of the argument quality of the information in the communication about the policy plan (hereafter: information manipulation). Per each policy, subjects were randomly allocated to one of two conditions of information: strong policy (i.e. logically persuasive policy plan) or weak policy (i.e. logically unpersuasive). Each subject was exposed to two policy plans, one strong and one weak, displayed in a random order. For instance, a subject who first received a strong air-pollution policy plan, later received the weak recycling policy plan, and vice versa. The information in the strong policy plan condition was taken from the EPM’s real work plan and from other official sources, whereas the information in the weak policy plan was fictional, and deliberately designed to create a poor policy plan, which is incompatible with achieving the policy goals.[^footnote_reliability_information_manipulation] The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix A**.

@@

In line with the abovementioned hypotheses, my main focus in this paper is on participants' trust in the air-pollution policy, and the two-way interactions between residence in Haifa Bay and the symbols and information manipulations of that policy. I also explore these interactions with regard to the recycling policy, and compare them to the air-pollution interactions. Additionally, within the Haifa Bay sample, I examine the two-way interactions between the relevance manipulation and the symbols and information manipulations.

@@

The outcome variable, citizens' trust in policy, is measured in the survey using a composite index of six items (Cronbach’s alpha = `r alpha_air_trust` for air-pollution policy, and `r alpha_waste_trust` for the recycling policy). This scale was adopted with modifications from validated trust scales used by previous public-administration studies [@karens_2016; @grimmelikhuijsen_2017; @grimmelikhuijsen_2018]. Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7 (strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.

@@

Living in Haifa Bay area was coded according to respondents’ reporting of residence, work or studying in one of the Haifa Bay cities. To confirm the empirical assumption that the air-pollution policy (but not the recycling policy) is perceived as more personally relevant by Haifa Bay residents compared with center residents, respondents were asked, after the outcome variable items: "To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much"). `r figure.x=figure.x+1`**Figure `r figure.x`** shows the distributions of the latter items across the two areas. As expected, the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents  (Cohen's D = `r relevance.areas.d[["estimate"]] %>% round(2)` [`r relevance.areas.d[["conf.int"]][["lower"]] %>% round(2)`,`r relevance.areas.d[["conf.int"]][["upper"]] %>% round(2)`]). By comparison, the recycling policy is perceived by both groups as relatively personally relevant by both groups, with no statistically significant differences between them. Additional support for these differences are provided by respondents' answers to the open question about the most salient environmental issue in their area of residence, which was presented to the relevance treatment group (i.e. before presenting the policy plans). Indeed, `r t1<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow()``r t1` of the `r t2<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow()``r t2` Haifa Bay subjects who were asked this question regarded in their responses to the air-pollution generated from the industrial area (`r air.content.percent.haifa <- t1/t2*100``r air.content.percent.haifa %>% round(0)`%).[^footnote_air_relevance_coding] Moreover, many Haifa Bay respondents explicitly linked the air-pollution to higher morbidity rates in their area. Subjects from center cities regarded to a variety of issues, including recycling, traffic jams and cleanliness, and only `r ((SVIVA2_01_center %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow())/nrow(SVIVA2_01_center)*100) %>% round(0)`% of them mentioned air-pollution as a prominent environmental concern in their area.

@@

I now turn to exploring the main outcome variable of interest -- respondents trust in the *air-pollution policy*. This outcome variable has a right-skewed distribution (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r sd.air %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`), which entails that more subjects reported very low levels of trust, than very high levels of trust in than policy. `r figure.x=figure.x+1`**Figure `r figure.x`** shows the means and distributions of the outcome variable across the different experimental conditions of symbolic elements and information, and across the two areas. The real symbols condition (in the left panel) has a positive and significant main effect on trust in that policy plan compared with the no symbols condition (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`). That effect amounts to `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`]. Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received fake symbols, yet these differences are not significant at the 95% level (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`, *p* = `r (t.symbols.fake[["p.value"]]) %>% abs() %>% round(.,3)`). The increase in the lower bound of the box in the real symbols shows that real symbols greatly reduced the number of participants who reported very low trust score. Descriptively, `r ((filter(SVIVA2_01,SYMBOL==0,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==0) %>% nrow()) *100) %>% round(1)`% of the participants in the no symbols group reported a score of 2 or less which indicates very low level of trust, compares with `r ((filter(SVIVA2_01,SYMBOL==1,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==1) %>% nrow()) *100) %>% round(1)`% and only `r ((filter(SVIVA2_01,SYMBOL==2,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==2) %>% nrow()) *100) %>% round(1)`% in the real symbols group. As shown in the middle panel, the main effect of the weak information condition is negative and significant (*diff* = `r (main.info %>% .[2,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.info[["conf.int"]][2]) %>% round(.,2)`-`r (t.info[["conf.int"]][1]) %>% round(.,2)`], *t* = `r t.info[["statistic"]][["t"]] %>% abs() %>% round(.,3)`). That effect amounts to `r ((main.info %>% .[2,"estimate"]*-1)/sd.air) %>% max(.) %>% round(.,2)` SDs [`r (t.info[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.info[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`]. Finally, as presented in the right panel, participants from Haifa Bay reported significantly lower levels of trust in the air-pollution policy, compared to center participants (*diff* = `r (main.areas %>% .[2,"estimate"]*-1) %>% max(.) %>% abs() %>% round(.,2)` [`r (t.areas[["conf.int"]][2]) %>% round(.,2) %>% abs()`-`r (t.areas[["conf.int"]][1]) %>% round(.,2) %>% abs()`], *t* = `r t.areas[["statistic"]][["t"]] %>% abs() %>% round(.,3)`). Descriptively, `r ((filter(SVIVA2_01_haifa,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_haifa))*100)%>%round(1)`% of Haifa Bay subjects have a trust-index score lower than 4, the scale's middle point (compared with `r ((filter(SVIVA2_01_center,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_center))*100)%>% round(1)`% of the center subjects). This indicates that the majority of the sampled Haifa Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area.

@@

I further examined the interactions between the manipulations and the two areas via a series of multiple linear regression models, presented in `r table.x=table.x+1`**Table `r table.x`**. I regress trust in air-pollution policy on the manipulations (Model `r table.x`.1), then I add the areas (Model `r table.x`.2) and the interaction between them (Model `r table.x`.3). In Model `r table.x`.4, I test the robustness of the interaction model by controlling for individual-level covariates.[^footnote_control_variables] In all regression models, I use robust standard errors to adjust for heteroskedacity.[^footnote_heteroskedacity] The results of these models are largely consistent with the raw findings presented above. In Models `r table.x`.3, `r table.x`.4 the interactions between living in the center and the real symbols are negative but not sufficiently significant, and the interactions with the weak information are insignificant. A comparison between models `r table.x`.2 and `r table.x`.3 via anova reveals that adding these interactions do not significantly improve the model fit (*F(`r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(df) %>% .[2,] %>% max()`*) = `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(statistic) %>% .[2,] %>% max() %>% round(2)`, *p*= `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(p.value) %>% .[2,] %>% max() %>% round(2)`).

@@

Overall, the findings with regard to the air-pollution policy indicate, tentatively, that higher levels of perceived personal relevance of the communication neither attenuate the positive effect of brand elements entangled in communications, nor enhances citizens' attention to their substantive content. Still, as discussed in the previous section, this analysis is based on the observational comparison between the areas and not by a random assignment, and hence a concern of endogeneity cannot be entirely ruled. Accordingly, the null findings regarding the interactions between the areas and the manipulations can be resulted by other, unobserved differences between the two populations. Yet, as explained, the experimental design provides two additional tests which enable to address this concern: the comparison to the recycling policy, for which there are no relevance differences between the two groups, and the relevance manipulation. I now discuss the results of these two tests.

@@

[^footnote_recycling_model]: The main effect of the real symbols (as depicted from Model 2.1) is significant compared with the no symbols group (*Diff*=`r diff1` [`r (diff1-1.96*se1) %>% round(3)`-`r (diff1+1.96*se1) %>% round(3)`], *t*=`r (diff1/se1) %>% round(3)`). Yet, the increase is not significant not with the fake symbols group (*Diff*=`r diff2` [`r (diff2-1.96*se2) %>% round(3)`-`r (diff2+1.96*se2) %>% round(3)`], *t*=`r (diff2/se2) %>% round(3)`). As shown in Model 2.3, the real symbols significantly increased Haifa Bay subjects' trust in that policy compared with the no symbols group (*Diff*=`r diff3` [`r (diff3-1.96*se3) %>% round(3)`-`r (diff3+1.96*se3) %>% round(3)`], *t*=`r (diff3/se3) %>% round(3)`), whereas the increase compared with the fake symbols group was not sufficiently significant (*Diff*=`r diff4` [`r (diff4-1.96*se4) %>% round(3)`-`r (diff4+1.96*se4) %>% round(3)`], *t*=`r (diff4/se4) %>% round(3)`). The differences between the symbols groups among the center subjects are small and insignificant. The weaker effect of the real symbols can be partly explained by the fact that I used a different celebrity campaign image for this policy, which was less familiar compared with the image presented for the air-pollution policy. The main effect of weak information (as depicted from Model 2.1) ammounts to `r (diff5/sd.waste) %>% round(3)` SDs [`r ((diff5-1.96*se5)/sd.waste) %>% round(3)`-`r ((diff5+1.96*se5)/sd.waste) %>% round(3)`]. In model 2.5, the interaction between weak information and the center area is positive, but far from significance.

@@

**Air-pollution policy** (Reducing the air-pollution in the Haifa Bay)

>>>>

Viewed against the above theoretical framework, symbolic elements in government communications can be regarded as peripheral cues, which can affect citizens' attitudes though a peripheral route process of evaluative conditioning.[^footnote_symbols_arguments] Hence, based on ELM, citizens judgements about public organizations are less likely to be affected by symbols (and more likely to be shaped by substantive arguments) the more motivated they are to critically think about the message. Citizens' level of motivation is likely to be determined, to a great extent, by their the degree in which they perceive the policy issue in the communication as having personal relevance for themselves.

@@

*H<sub>1</sub> - Symbolic elements in communications are likely to have a greater positive effect on citizens' attitudes about government organizations and policies, the lower the perceived personal relevance of the communication.*

*H<sub>2</sub> - The argument quality of the information in communications is likely to have a weaker effect on citizens' attitudes about government organizations and policies, the lower the perceived personal relevance of the communication.*

@@

While comparing those residing in the Haifa Bay to others enables me to examine the moderating effect of perceived personal relevance, it still has an important limitation - it represents an observational comparison. The differences in personal relevance can be theoretically confounded by unobserved covariates, that cannot be effectively controlled in the analyses. I address this limitation in the research design in three main ways. *First*, in the selection of the research population, I sought to reduce differences in socioeconomic and demographic variables between residents of Haifa Bay, and their comparison group. Accordingly, I selected the major cities in the Haifa Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*,[^footnote_qiryat-Hayiim] *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*). The socioeconomic characteristics of these selected cities are summarized in the supplementary appendix (section ##). I further searched relevant EPM documents and news websites and confirmed that there no particular reporting about high air-pollution levels in the three center cities.

*Second*, in addition to the policy regarding the Haifa Bay air-pollution, I also included in the experiment a second policy plan that is expected to be perceived by the two groups as equally relevant. For this purpose, I selected a policy plan of EPM that regards *reducing domestic waste and increasing recycling*. The comparison between the two EPM policies is intended to confirm that respondents’ divergent responses to symbolic elements in the communication of the first policy, if found, are attributed to differences in perceived personal relevance, and not to other covariates. I henceforth refer to these two policy plans as "Haifa Bay air-pollution" and "recycling". *Third*, in addition to the observational comparison between the two areas, I also included an experimental manipulation aimed at enhancing the perceived personal relevance of the air-pollution policy among the Haifa Bay residents.

@@

[^footnote_relevance_manipulation]: The first three treatment questions were also initially designed to prime subjects, more generally, to think about the impact of environmental issues to their own lives. In this paper, I focus on the the moderating effect of the relevance manipulation on Haifa Bay citizens' responses to the Haifa Bay air-pollution policy.

Participants were then presented with the air-pollution and recycling policy plans (displayed in a random order). They were informed that these plans were obtained from EPM's annual work plan. The participants were randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols manipulation): treatment ("real symbols"), control-"no symbols" and control-"fake symbols". In the real symbols condition, the two policies are displayed with three symbolic brand elements, which have been used in EPM's public communications, and became widely recognized by the public. The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment. The second element is the green color, which is strongly associated with taking care of the environment. The third element is an image of a celebrity comedian from an advertising campaign of the EPM. The Haifa Bay air-pollution policy (in the real symbols condition) was presented with an image from EPM campaign from 2010 under the slogan "starting to think green", starring the Israeli celebrity comedian Tal Friedman. The recycling policy (in the real symbols condition) was presented with an image from a campaign from 2017 for reducing the use of disposable bags ("taking every bag seriously"), starring the comedian Ido Rosenblum. In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities’ images. Finally, in the control fake-symbols condition, the EPM logo is replaced by a fake logo, the green color is replaced with blue, and the images of celebrities from the campaigns are replaced with edited images of unfamiliar people. The purpose of the fake-logo condition was to distinguish the effect of the symbolic meaning of the EPM's graphic brand elements (i.e. the symbolic effect) from a possible effect of their aesthetic design. Accordingly, I specifically designed the "fake" symbols so that they would resemble the real symbols and have equivalent aesthetic qualities, without activating particular emotions and associations related to EPM, or environmental policy. The symbols conditions are displayed in **Appendix B**. Further details about the real and fake symbols are found in section ## of the supplementary appendix.

In addition, I also included a manipulation of the argument quality of the information in the communication about the policy plan (hereafter: information manipulation). Per each policy, subjects were randomly allocated to one of two conditions of information: strong policy (i.e. logically persuasive policy plan) or weak policy (i.e. logically unpersuasive). Each subject was exposed to two policy plans, one strong and one weak, displayed in a random order. For instance, a subject who first received a strong Haifa Bay air-pollution policy plan, later received the weak recycling policy plan, and vice versa. The information in the strong policy plan condition was taken from the EPM’s real work plan and from other official sources, whereas the information in the weak policy plan was fictional, and deliberately designed to create a poor policy plan, which is incompatible with achieving the policy goals.[^footnote_reliability_information_manipulation] The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix A**.

@@

In line with the abovementioned hypotheses, my main focus in this paper is on participants' trust in the Haifa Bay air-pollution policy, and the two-way interactions between residence in Haifa Bay and the symbols and information manipulations of that policy. I also explore these interactions with regard to the recycling policy, and compare them to the air-pollution interactions. Additionally, within the Haifa Bay sample, I examine the two-way interactions between the relevance manipulation and the symbols and information manipulations.

@@

The outcome variable, citizens' trust in policy, is measured in the survey using a composite index of six items (Cronbach’s alpha = `r alpha_air_trust` for Haifa Bay air-pollution policy, and `r alpha_waste_trust` for the recycling policy). This scale was adopted with modifications from validated trust scales used by previous public-administration studies [@karens_2016; @grimmelikhuijsen_2017; @grimmelikhuijsen_2018]. Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7 (strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.

@@

Living in Haifa Bay area was coded according to respondents’ reporting of residence, work or studying in one of the Haifa Bay cities. To confirm the empirical assumption that the Haifa Bay air-pollution policy (but not the recycling policy) is perceived as more personally relevant by Haifa Bay residents compared with center residents, respondents were asked, after the outcome variable items: "To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much"). `r figure.x=figure.x+1`**Figure `r figure.x`** shows the distributions of the latter items across the two areas. As expected, the Haifa Bay air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents  (Cohen's D = `r relevance.areas.d[["estimate"]] %>% round(2)` [`r relevance.areas.d[["conf.int"]][["lower"]] %>% round(2)`,`r relevance.areas.d[["conf.int"]][["upper"]] %>% round(2)`]). By comparison, the recycling policy is perceived by both groups as relatively personally relevant by both groups, with no statistically significant differences between them. Additional support for these differences are provided by respondents' answers to the open question about the most salient environmental issue in their area of residence, which was presented to the relevance treatment group (i.e. before presenting the policy plans). Indeed, `r t1<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow()``r t1` of the `r t2<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow()``r t2` Haifa Bay subjects who were asked this question regarded in their responses to the air-pollution generated from the industrial area (`r air.content.percent.haifa <- t1/t2*100``r air.content.percent.haifa %>% round(0)`%).[^footnote_air_relevance_coding] Moreover, many Haifa Bay respondents explicitly linked the air-pollution to higher morbidity rates in their area. Subjects from center cities regarded to a variety of issues, including recycling, traffic jams and cleanliness, and only `r ((SVIVA2_01_center %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow())/nrow(SVIVA2_01_center)*100) %>% round(0)`% of them mentioned air-pollution as a prominent environmental concern in their area.

@@

I now turn to exploring the main outcome variable of interest -- respondents trust in the *Haifa Bay air-pollution policy*. This outcome variable has a right-skewed distribution (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r sd.air %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`), which entails that more subjects reported very low levels of trust, than very high levels of trust in than policy. `r figure.x=figure.x+1`**Figure `r figure.x`** shows the means and distributions of the outcome variable across the different experimental conditions of symbolic elements and information, and across the two areas. The real symbols condition (in the left panel) has a positive and significant main effect on trust in that policy plan compared with the no symbols condition (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`). That effect amounts to `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`]. Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received fake symbols, yet these differences are not significant at the 95% level (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`, *p* = `r (t.symbols.fake[["p.value"]]) %>% abs() %>% round(.,3)`). The increase in the lower bound of the box in the real symbols shows that real symbols greatly reduced the number of participants who reported very low trust score. Descriptively, `r ((filter(SVIVA2_01,SYMBOL==0,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==0) %>% nrow()) *100) %>% round(1)`% of the participants in the no symbols group reported a score of 2 or less which indicates very low level of trust, compares with `r ((filter(SVIVA2_01,SYMBOL==1,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==1) %>% nrow()) *100) %>% round(1)`% and only `r ((filter(SVIVA2_01,SYMBOL==2,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==2) %>% nrow()) *100) %>% round(1)`% in the real symbols group. As shown in the middle panel, the main effect of the weak information condition is negative and significant (*diff* = `r (main.info %>% .[2,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.info[["conf.int"]][2]) %>% round(.,2)`-`r (t.info[["conf.int"]][1]) %>% round(.,2)`], *t* = `r t.info[["statistic"]][["t"]] %>% abs() %>% round(.,3)`). That effect amounts to `r ((main.info %>% .[2,"estimate"]*-1)/sd.air) %>% max(.) %>% round(.,2)` SDs [`r (t.info[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.info[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`]. Finally, as presented in the right panel, participants from Haifa Bay reported significantly lower levels of trust in the Haifa Bay air-pollution policy, compared to center participants (*diff* = `r (main.areas %>% .[2,"estimate"]*-1) %>% max(.) %>% abs() %>% round(.,2)` [`r (t.areas[["conf.int"]][2]) %>% round(.,2) %>% abs()`-`r (t.areas[["conf.int"]][1]) %>% round(.,2) %>% abs()`], *t* = `r t.areas[["statistic"]][["t"]] %>% abs() %>% round(.,3)`). Descriptively, `r ((filter(SVIVA2_01_haifa,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_haifa))*100)%>%round(1)`% of Haifa Bay subjects have a trust-index score lower than 4, the scale's middle point (compared with `r ((filter(SVIVA2_01_center,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_center))*100)%>% round(1)`% of the center subjects). This indicates that the majority of the sampled Haifa Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area.

@@

I further examined the interactions between the manipulations and the two areas via a series of multiple linear regression models, presented in `r table.x=table.x+1`**Table `r table.x`**. I regress trust in Haifa Bay air-pollution policy on the manipulations (Model `r table.x`.1), then I add the areas (Model `r table.x`.2) and the interaction between them (Model `r table.x`.3). In Model `r table.x`.4, I test the robustness of the interaction model by controlling for individual-level covariates.[^footnote_control_variables] In all regression models, I use robust standard errors to adjust for heteroskedacity.[^footnote_heteroskedacity] The results of these models are largely consistent with the raw findings presented above. In Models `r table.x`.3, `r table.x`.4 the interactions between living in the center and the real symbols are negative but not sufficiently significant, and the interactions with the weak information are insignificant. A comparison between models `r table.x`.2 and `r table.x`.3 via anova reveals that adding these interactions do not significantly improve the model fit (*F(`r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(df) %>% .[2,] %>% max()`*) = `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(statistic) %>% .[2,] %>% max() %>% round(2)`, *p*= `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(p.value) %>% .[2,] %>% max() %>% round(2)`).

@@

Overall, the findings with regard to the Haifa Bay air-pollution policy indicate, tentatively, that higher levels of perceived personal relevance of the communication neither attenuate the positive effect of brand elements entangled in communications, nor enhances citizens' attention to their substantive content. Still, as discussed in the previous section, this analysis is based on the observational comparison between the areas and not by a random assignment, and hence a concern of endogeneity cannot be entirely ruled. Accordingly, the null findings regarding the interactions between the areas and the manipulations can be resulted by other, unobserved differences between the two populations. Yet, as explained, the experimental design provides two additional tests which enable to address this concern: the comparison to the recycling policy, for which there are no relevance differences between the two groups, and the relevance manipulation. I now discuss the results of these two tests.

@@

[^footnote_recycling_model]: The main effect of the real symbols (as depicted from Model 2.1) is significant compared with the no symbols group (*Diff*=`r diff1` [`r (diff1-1.96*se1) %>% round(3)`-`r (diff1+1.96*se1) %>% round(3)`], *t*=`r (diff1/se1) %>% round(3)`). Yet, the increase is not significant not with the fake symbols group (*Diff*=`r diff2` [`r (diff2-1.96*se2) %>% round(3)`-`r (diff2+1.96*se2) %>% round(3)`], *t*=`r (diff2/se2) %>% round(3)`). As shown in Model 2.3, the real symbols significantly increased Haifa Bay subjects' trust in that policy compared with the no symbols group (*Diff*=`r diff3` [`r (diff3-1.96*se3) %>% round(3)`-`r (diff3+1.96*se3) %>% round(3)`], *t*=`r (diff3/se3) %>% round(3)`), whereas the increase compared with the fake symbols group was not sufficiently significant (*Diff*=`r diff4` [`r (diff4-1.96*se4) %>% round(3)`-`r (diff4+1.96*se4) %>% round(3)`], *t*=`r (diff4/se4) %>% round(3)`). The differences between the symbols groups among the center subjects are small and insignificant. The weaker effect of the real symbols can be partly explained by the fact that I used a different celebrity campaign image for this policy, which was less familiar compared with the image presented for the Haifa Bay air-pollution policy. The main effect of weak information (as depicted from Model 2.1) ammounts to `r (diff5/sd.waste) %>% round(3)` SDs [`r ((diff5-1.96*se5)/sd.waste) %>% round(3)`-`r ((diff5+1.96*se5)/sd.waste) %>% round(3)`]. In model 2.5, the interaction between weak information and the center area is positive, but far from significance.

@@

**Haifa Bay air-pollution policy** (Reducing the air-pollution in the Haifa Bay)
